Methods

### 2024-10-17 pages/background.qmd
docs(background): add baker 2016
docs(background): add some extra background citations, and citations that inspired protocol

>>>>

## General context

@baker_1500_2016 - survey of 1576 researchers across disciplines, finding:

* "More than 70% of researchers have tried and failed to reproduce another scientist's experiments"
* "More than half have failed to reproduce their own experiments"
* 52% "agree that there is a significant 'crisis' of reproducibility"
* "Less than 31% think that failure to reproduce published results means that the result is probably wrong, and most say that they still trust the published literature"

Differences between **reproduction** and **replication**

* Reproduction - using their code
* Replication - writing your own code

@korbmacher_replication_2023 - great discussion of the **replication** crisis

On the [protocol page](protocol.qmd), several reproducibility studies are mentioned, which were used to help inform the methods in our reproducibility assessments.

### 2024-10-17 pages/protocol.qmd
docs(background): add some extra background citations, and citations that inspired protocol

>>>>

## Inspiration

As cited in @heather_protocol_2024, the protocol was informed by several prior studies assessing computational reproducibility:

* @krafczyk_learning_2021: Assessed the reproducibility of seven articles published in the Journal of Computational Physics.
* @wood_push_2018 and @wood_replication_2018: Assessed the reproducibility of 109 published impact evaluations in low- and middle-income countries. Conducted in association with the replication programme of the International Initiative for Impact Evaluation (3ie).
* @schwander_replication_2021: Assessed the reproducibility of four health economic obesity models.
* @laurinavichyute_share_2022: Assessed the reproducibility of 118 articles published in the Journal of Memory and Language.
* @konkol_computational_2019: Assessed the reproducibility of 41 geoscientific articles from Copernicus Publications and the Journal of Statistical Software.

It was also informed by:

* @ayllon_keeping_2021: Article with recommendations on keeping modelling notebooks to support completion of TRACE (TRAnsparent and Comprehensive model Evaluation) documents.
* @berkeley_initiative_for_transparency_in_the_social_sciences_guide_2022: Guidelines on conducting reproductions of published social science research.
* @mcmanus_can_2019: Article proposing several possible definitions for success in reproducing or replicating models in health economics.
* @marwick_packaging_2018: Article recommending how to structure data analytical work as research compendiums using the R package structure.
